Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2024-06-03 paper.qmd
Preparing stage 2 registered report

```{r}
source('functions.R')
source('pilot_analysis.R')
source('simulate.R')
source('sexspecificmodels.R')
source('stage2_analysis.R')
```

>>>>

```{r}
library(ggcorrplot)
library(tinytable)
library(patchwork)
source('functions.R')
source('pilot_analysis.R')
source('simulate.R')
source('sexspecificmodels.R')
```
